### 2021-05-11 shared/analysis.tex
WIP : Assert Violation

\begin{figure}
	\begin{equation}	
		Objective = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \mid \forall (i, j) [{x_i} \neq {x_j}]
	\end{equation}
	\caption{Optimization Expression for $k$ randomized paths}
	\label{eq:optimization-1}
\end{figure}

@@

For best approximation of the expected value of heads in $n$ trials,
\begin{equation}	
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i})
\end{equation}
where both $w_i$ and $sum_i$ can both be computed from the corresponding $\vec{d_i}$ expression we get from the $model$  of the $optimization$ query Eq~\ref{eq:optimization-1}

@@

Specify the \texttt{renaming} and \texttt{constraint} solving over the \texttt{optimization} expression. Write out this algorithm formally. \\

For $k = 5$, the five \texttt{constraint} sets and \texttt{optimization} expressions are : ...
\end{document}

>>>>

\begin{figure}
	\begin{equation}	
		Objective = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \quad \mid \forall (i, j) [{x_i} \neq {x_j}]
	\end{equation}
	\caption{Optimization Expression for $k$ randomized paths}
	\label{eq:optimization-1}
\end{figure}

@@

For best approximation of the expected value of heads in $n$ trials,
\begin{equation}	
	w_i = \prod_{j=1}^n choice\_prob_{i}(j) ,
	\quad
	sum_i = \sum_{j=1}^n components(\vec{d_i}) ,
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
	\quad
	Error = n * prob - EV(heads)
\end{equation}
where both $w_i$ and $sum_i$ can both be computed from the corresponding $\vec{d_i}$ expression we get from the $model$  of the $optimization$ query Eq~\ref{eq:optimization-1}

@@

For $k = 5$ \& $n = 10$ the two \texttt{constraint} sets and \texttt{optimization} expressions are as follows :

\begin{equation}	
	w_1 = \prod_{j=1}^{10} choice\_prob_{1}(j) ,
	\quad
	sum_1 = \sum_{j=1}^{10} components(\vec{d_1}) ,
\end{equation}
\begin{equation}	
	w_2 = \prod_{j=1}^{10} choice\_prob_{2}(j) ,
	\quad
	sum_2 = \sum_{j=1}^{10} components(\vec{d_2}) ,
\end{equation}
\begin{equation}	
	w_3 = \prod_{j=1}^{10} choice\_prob_{3}(j) ,
	\quad
	sum_3 = \sum_{j=1}^{10} components(\vec{d_3}) ,
\end{equation}
\begin{equation}	
	w_4 = \prod_{j=1}^{10} choice\_prob_{4}(j) ,
	\quad
	sum_4 = \sum_{j=1}^{10} components(\vec{d_4}) ,
\end{equation}
\begin{equation}	
	w_5 = \prod_{j=1}^{10} choice\_prob_{5}(j) ,
	\quad
	sum_5 = \sum_{j=1}^{10} components(\vec{d_5}) ,
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
\end{equation}
\begin{equation}
	\enspace
	EV(heads) = (w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\begin{equation}
	\enspace
	Objective = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\end{document}
